The impact of information about tobacco-related reproductive vs. general health risks on South Indian women's tobacco use decisions

### 2020-08-22 paper.Rmd
Flesh out README with instructions for reproducing the analysis and paper.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10, scipen=99999)
source('analysis.R')
source('power.R')
library(knitr)
library(patchwork)
library(huxtable)
# library(gtsummary)
library(modelsummary)
library(broom.mixed)
```

@@

tmp4 <- custom.summarize(tmp3, vars, facvar = 'Time')
tmp5 <- as_hux(tmp4)
# tmp5 <- set_number_format(tmp5, )
tmp5 <- add_colnames(tmp5)
tmp5 <- rbind(c("", "Baseline", rep("", 2), "Followup", rep("", 4)), tmp5)
tmp5 <- merge_cells(tmp5, 1, 5:9)
caption(tmp5) <- "(#tab:summarystats) Summary statistics for sample demographics and key outcome variables for original sample and those remaining at followup (d: Cohen's d for mean difference; p: p-value for mean difference)."
tmp5

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10, scipen=99999)
if (!dir.exists('Figures')) dir.create('Figures')
source('analysis.R')
source('power.R')
library(knitr)
library(patchwork)
library(huxtable)
# library(gtsummary)
library(modelsummary)
library(broom.mixed)
```

@@

tmp4 <- custom.summarize(tmp3, vars, facvar = 'Time')
tmp5 <- as_hux(tmp4)
# tmp5 <- set_number_format(tmp5, )
tmp5 <- add_colnames(tmp5)
tmp5 <- rbind(c("", "Baseline", rep("", 2), "Followup", rep("", 4)), tmp5)
tmp5 <- merge_cells(tmp5, 1, 5:9)
caption(tmp5) <- "Summary statistics for sample demographics and key outcome variables for original sample and those remaining at followup (d: Cohen's d for mean difference; p: p-value for mean difference)."
tmp5
